---
title: "Commodities Report"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    theme: flatly
    highlight: kate
    self_contained: true
    css: "/Users/benjaminlachavanne/Desktop/script/finance_analysis/html/style/style.css"


params:
  llm_analysis: false
  
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Main path 
path_main <- file.path("~", "Desktop", "script", "finance_analysis")

# Upload packages, functions and inputs 
source(paste0(path_main,"/initialization/package.R"))         # |Package|
source(paste0(path_main,"/function/function_information.R"))  # |Function price|
source(paste0(path_main,"/function/function_format.R"))       # |Function format|
source(paste0(path_main,"/function/function_visualization.R"))        # |Functions visualization|
source(paste0(path_main,"/function/function_compute.R"))      # |Functions indicator|
source(paste0(path_main,"/function/function_ai.R"))           # |Functions ai|
source(paste0(path_main,"/initialization/input.R"))           # |Input|

# Download all series from the RDS folder
path_rds_folder    <- "/Users/benjaminlachavanne/Desktop/script/finance_analysis/database/rds/"
path_rds_all <- paste0(path_rds_folder,"series_store_all.rds")
series_database <- readRDS(path_rds_all)

# Styled info box
series_info_box <- function(source_html, frequency, adjustment, about) {
  htmltools::HTML(paste0('
  <div class="info-card">
    <div class="info-grid">
      <div class="info-row">
        <span class="info-label">Source</span>
        <span class="info-value">', source_html, '</span>
      </div>
      <div class="info-row">
        <span class="info-label">Frequency</span>
        <span class="info-value">', frequency, '</span>
      </div>
      <div class="info-row">
        <span class="info-label">Adjustment</span>
        <span class="info-value">', adjustment, '</span>
      </div>
    </div>
    <div class="info-about">', about, '</div>
  </div>
  '))
}

# Section label helper
section_label <- function(icon, text) {
  htmltools::HTML(paste0(
    '<div class="section-label"><span class="section-icon">', icon,
    '</span><span class="section-text">', text, '</span></div>'))
}

# Subsection label helper
subsection_label <- function(text) {
  htmltools::HTML(paste0('<div class="subsection-label">', text, '</div>'))
}

# Chart note helper
chart_note <- function(text) {
  htmltools::HTML(paste0('<p class="chart-note">', text, '</p>'))
}
```


<!-- ####################################################################### -->
<!-- Head Title  -->
<!-- ####################################################################### -->

```{=html}
<!-- ── MASTHEAD ─────────────────────────────────────────────────────────────── -->
<div class="masthead">
  <div class="masthead-eyebrow">Commodities Research · Global Markets</div>
  <div class="masthead-title">Commodities <span>Report</span></div>
  <div class="masthead-date">Latest update date: `r format(Sys.Date(), '%B %d, %Y')`</div>
</div>
```

<!-- ####################################################################### -->
<!-- Abstract  -->
<!-- ####################################################################### -->

## Abstract

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Abstract</div>
  </div>
</div>
```

```{=html}
<div class="abstract-box">
<p>This report provides a comprehensive overview of global commodity markets through a structured set of price and trend indicators covering the world's major futures contracts.</p>

<ul>
  <li>The <strong>World Commodities</strong> section opens with a summary table comparing performance across all tracked markets, followed by individual charts for each contract with moving average overlays.</li>
  <li>Coverage spans <strong>Energy</strong> (Brent Crude, WTI Crude, Natural Gas, Heating Oil, RBOB Gasoline), <strong>Metals</strong> (Gold, Silver, Copper, Platinum, Palladium, Aluminium), and <strong>Agriculture</strong> (Corn, Wheat, Soybeans, Coffee, Cocoa, Cotton, Sugar, Live Cattle, Lean Hogs, Orange Juice, Lumber).</li>
  <li>A <strong>Comparison</strong> section enables cross-sector performance analysis, followed by <strong>Commodity Indices</strong> (S&amp;P GSCI, Bloomberg Commodity Index) providing a broad synthetic view of the asset class.</li>
</ul>

<p>Taken together, this report aims to offer a 360° view of global commodity market dynamics, combining price signals with moving averages to support a comprehensive assessment of the current environment.</p>
</div>
```

<!-- ####################################################################### -->
<!-- World Commodities  -->
<!-- ####################################################################### -->

## World Commodities

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">World Commodities</div>
  </div>
</div>
```

```{r COMMODITIES TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/" target="_blank">link</a> · Investing.com — <a href="https://www.investing.com/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about  = '
  This table presents the performance of major global commodity futures across multiple time horizons
  (1 day, 5 days, 1 month, 3 months, 6 months, 1 year, 2 years, 5 years and since inception).
  It covers the following contracts:
  <br><br>
  <b>Energy:</b> Brent Crude <i>(global oil benchmark)</i> ·
  WTI Crude <i>(U.S. oil benchmark)</i> ·
  Natural Gas <i>(Henry Hub front contract)</i> ·
  Heating Oil <i>(distillate benchmark)</i> ·
  RBOB Gasoline <i>(gasoline benchmark)</i>
  <br><br>
  <b>Metals:</b> Gold <i>(COMEX)</i> · Silver <i>(COMEX)</i> ·
  Copper <i>(COMEX)</i> · Platinum <i>(NYMEX)</i> ·
  Palladium <i>(NYMEX)</i> · Aluminium <i>(COMEX)</i>
  <br><br>
  <b>Agriculture:</b> Corn <i>(CBOT)</i> · Wheat <i>(CBOT)</i> ·
  Soybeans <i>(CBOT)</i> · Coffee <i>(Arabica, ICE)</i> ·
  Cocoa <i>(ICE)</i> · Cotton <i>(ICE)</i> · Sugar <i>(ICE No.11)</i> ·
  Live Cattle <i>(CME)</i> · Lean Hogs <i>(CME)</i> ·
  Orange Juice <i>(ICE)</i> · Lumber <i>(CME)</i>
  <br><br>
  <b>Commodity Indices:</b> S&amp;P GSCI <i>(broad commodity index)</i> ·
  Bloomberg Commodity Index <i>(BCOM)</i>
  '
)
```

### Table

```{=html}
<div class="perf-section">
```

```{r COMMODITIES TABLE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Mapping tickers to readable names
labels <- c(
  "BZ=F"    = "Brent Crude Oil",
  "CL=F"    = "WTI Crude Oil",
  "NG=F"    = "Natural Gas",
  "HO=F"    = "Heating Oil",
  "RB=F"    = "RBOB Gasoline",
  "GC=F"    = "Gold",
  "SI=F"    = "Silver",
  "HG=F"    = "Copper",
  "PL=F"    = "Platinum",
  "PA=F"    = "Palladium",
  "ALI=F"   = "Aluminium",
  "ZC=F"    = "Corn",
  "ZW=F"    = "Wheat",
  "ZS=F"    = "Soybeans",
  "KC=F"    = "Coffee (Arabica)",
  "CC=F"    = "Cocoa",
  "CT=F"    = "Cotton",
  "SB=F"    = "Sugar",
  "LE=F"    = "Live Cattle",
  "HE=F"    = "Lean Hogs",
  "OJ=F"    = "Orange Juice",
  "LBS=F"   = "Lumber"
)

# Get series
commodities <- c("BZ=F","CL=F","NG=F","HO=F","RB=F",
                 "GC=F","SI=F","HG=F","PL=F","PA=F","ALI=F",
                 "ZC=F","ZW=F","ZS=F","KC=F","CC=F","CT=F","SB=F","LE=F","HE=F","OJ=F","LBS=F")

# Plot table
div(style = "display: flex; justify-content: center;",
    produce_performance_table(series = commodities, label = labels))
```

```{=html}
</div>
```

### Comparison

#### *Energy*

```{=html}
<div class="perf-section">
```

```{r COMMO COMP ENERGY, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_brent_crude", "fut_wti_crude", "fut_natural_gas", "fut_heating_oil", "fut_rbob_gasoline"))

# Compute index
data <- compute_rebase(df = data, base = "2015-01-07")

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "Energy Futures – Indexed Performance (2015:01:07 = 100)"))
```

```{=html}
</div>
```

#### *Metals*

```{=html}
<div class="perf-section">
```

```{r COMMO COMP METALS, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_gold", "fut_silver", "fut_copper", "fut_platinum", "fut_palladium", "fut_aluminium"))

# Compute index
data <- compute_rebase(df = data, base = "2015-01-07")

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "Metals Futures – Indexed Performance (2015:01:07 = 100)"))
```

```{=html}
</div>
```

#### *Agriculture*

```{=html}
<div class="perf-section">
```

```{r COMMO COMP AGRI, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_corn", "fut_wheat", "fut_soybeans", "fut_coffee", "fut_cocoa", "fut_cotton", "fut_sugar", "fut_live_cattle", "fut_lean_hogs", "fut_orange_juice", "fut_lumber"))

# Compute index
data <- compute_rebase(df = data, base = "2015-01-07")

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "Agriculture Futures – Indexed Performance (2015:01:07 = 100)"))
```

```{=html}
</div>
```

### Indices

#### *S&P GSCI*

```{r IDX SPGSCI TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/%5ESPGSCI/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "The S&P GSCI is a broad, production-weighted commodity index maintained by S&P Dow Jones Indices, covering energy, metals, and agriculture. Its heavy energy weighting (typically 50–70%) means it closely tracks oil market dynamics. Widely used as a benchmark for broad commodity exposure and as an inflation sensitivity gauge. Quoted in index points, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r IDX SPGSCI, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("idx_spgsci"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

#### *Bloomberg Commodity Index*

```{r IDX BCOM TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Investing.com — <a href="https://www.investing.com/indices/bloomberg-commodity" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "The Bloomberg Commodity Index (BCOM) tracks a diversified basket of commodity futures across energy, metals, and agriculture, with sector caps limiting any single group to 33% and any single commodity to 15%. Its more balanced weighting relative to the S&P GSCI makes it a preferred benchmark for diversified commodity exposure without undue energy concentration. Quoted in index points, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r IDX BCOM, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("idx_bcom"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

<!-- ####################################################################### -->
<!-- Energy  -->
<!-- ####################################################################### -->

## Energy

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Energy</div>
  </div>
</div>
```

### Brent Crude Oil

```{r ENERGY BRENT TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/BZ=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Brent Crude is the international oil benchmark, sourced from the North Sea and priced in USD per barrel. It serves as the reference price for roughly two-thirds of global crude oil trading. Sensitive to OPEC+ supply decisions, geopolitical tensions, and global demand conditions. Quoted in USD per barrel, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r ENERGY BRENT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_brent_crude"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### WTI Crude Oil

#### Price 

```{r ENERGY WTI TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/CL=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "WTI (West Texas Intermediate) is the primary U.S. oil benchmark, produced in the Permian Basin and delivered at Cushing, Oklahoma. It trades at a spread to Brent, influenced by U.S. production dynamics, pipeline infrastructure, and domestic inventory levels. Sensitive to Fed policy, the U.S. dollar, and shale production costs. Quoted in USD per barrel, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r ENERGY WTI, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_wti_crude"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

#### Drivers

```{r INV WTI TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Investing.com — <a href="https://www.investing.com/economic-calendar/eia-crude-oil-inventories-75" target="_blank">link</a>',
  frequency = "Weekly",
  adjustment = "Not Adjusted",
  about = "U.S. crude oil inventories as reported weekly by the EIA (Energy Information Administration). Stocks are measured in thousands of barrels and cover commercial crude oil held at refineries, tank farms, and pipelines, excluding the Strategic Petroleum Reserve (SPR). A key fundamental driver of WTI prices: rising inventories signal oversupply and typically pressure prices lower, while declining stocks indicate tightening conditions and support higher prices. The Cushing, Oklahoma hub, the physical delivery point for WTI futures, is particularly closely watched.")
```


```{r INV WTI, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("us_crude_inv"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = FALSE)))
```


### Natural Gas

```{r ENERGY NATGAS TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/NG=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "The Henry Hub Natural Gas futures contract is the U.S. benchmark for natural gas, priced at the Henry Hub pipeline interconnection in Louisiana. Highly volatile and seasonally driven, it is sensitive to weather conditions, storage levels, LNG export demand, and power generation needs. Quoted in USD per MMBtu, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r ENERGY NATGAS, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_natural_gas"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Heating Oil

```{r ENERGY HO TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/HO=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Heating Oil futures track No. 2 distillate fuel, a key refined petroleum product used for residential heating and as a diesel fuel proxy. Listed on NYMEX, it is closely correlated with crude oil prices and refinery margins. Demand is highly seasonal, peaking in Northern Hemisphere winters. Quoted in USD per gallon, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r ENERGY HO, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_heating_oil"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### RBOB Gasoline

```{r ENERGY RBOB TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/RB=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "RBOB Gasoline futures represent the U.S. benchmark for unleaded gasoline, listed on NYMEX. Prices are driven by crude oil input costs, refinery utilization, seasonal demand (summer driving season), and U.S. inventory data. Closely tracked as an indicator of downstream energy consumer conditions. Quoted in USD per gallon, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r ENERGY RBOB, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_rbob_gasoline"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

<!-- ####################################################################### -->
<!-- Metals  -->
<!-- ####################################################################### -->

## Metals

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Metals</div>
  </div>
</div>
```

### Gold

```{r METALS GOLD TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/GC=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Gold futures (COMEX front contract) represent the primary global benchmark for the precious metal. Gold serves as a safe-haven asset, inflation hedge, and monetary reserve, making it sensitive to real interest rates, the U.S. dollar, geopolitical risk, and central bank demand. Quoted in USD per troy ounce, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r METALS GOLD, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_gold"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Silver

```{r METALS SILVER TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/SI=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Silver futures (COMEX front contract) combine monetary and industrial characteristics, making silver more volatile than gold. Demand is driven by both investment flows and industrial applications including solar panels, electronics, and medical devices. Particularly sensitive to global manufacturing activity alongside traditional precious metal drivers. Quoted in USD per troy ounce, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r METALS SILVER, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_silver"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Copper

```{r METALS COPPER TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/HG=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Copper futures (COMEX front contract) are widely regarded as a leading indicator of global economic activity given the metal's pervasive use in construction, electrical infrastructure, and manufacturing. Prices are heavily influenced by Chinese demand, global industrial output, and mine supply from major producers such as Chile and Peru. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r METALS COPPER, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_copper"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Platinum

```{r METALS PLATINUM TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/PL=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Platinum futures track one of the rarest precious metals, with applications concentrated in automotive catalytic converters, jewelry, and industrial processes. Supply is highly concentrated in South Africa and Russia, creating significant geopolitical supply risk. Prices are sensitive to automotive sector trends and the ongoing energy transition. Quoted in USD per troy ounce, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r METALS PLATINUM, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_platinum"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Palladium

```{r METALS PALLADIUM TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/PA=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Palladium futures track a precious metal primarily used in gasoline-engine catalytic converters, with supply overwhelmingly concentrated in Russia and South Africa. It has been among the most volatile precious metals, driven by automotive demand trends, emission regulation tightening, and ongoing substitution dynamics with platinum. Quoted in USD per troy ounce, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r METALS PALLADIUM, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_palladium"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Aluminium

```{r METALS ALU TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/ALI=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Aluminium futures (COMEX front contract) track the world's most widely used non-ferrous metal, with applications spanning transportation, construction, packaging, and electrical cables. Prices are heavily influenced by Chinese smelter output, energy costs (aluminium smelting is extremely energy-intensive), and global industrial demand. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r METALS ALU, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_aluminium"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

<!-- ####################################################################### -->
<!-- Agriculture  -->
<!-- ####################################################################### -->

## Agriculture

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Agriculture</div>
  </div>
</div>
```

### Corn

```{r AGRI CORN TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/ZC=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Corn futures (CBOT front contract) represent the world's most widely produced grain, used for animal feed, ethanol, and food processing. The U.S. is the largest producer and exporter, making prices sensitive to U.S. crop conditions, weather patterns, ethanol policy, and competition from South American harvests. Quoted in USD per bushel, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI CORN, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_corn"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Wheat

```{r AGRI WHEAT TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/ZW=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Wheat futures (CBOT front contract) track the primary staple grain used for bread, pasta, and animal feed. Global supply is diversified across the U.S., Russia, Ukraine, Australia, and the EU. Prices are particularly sensitive to Black Sea production and export flows, weather disruptions, and geopolitical events in key growing regions. Quoted in USD per bushel, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI WHEAT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_wheat"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Soybeans

```{r AGRI SOY TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/ZS=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Soybean futures (CBOT front contract) represent the world's leading oilseed, crushed into soybean meal for animal feed and soybean oil for food and biodiesel. The U.S. and Brazil are the dominant producers, and prices are highly sensitive to Chinese import demand, South American crop conditions, and U.S.-China trade relations. Quoted in USD per bushel, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI SOY, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_soybeans"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Coffee

```{r AGRI COFFEE TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/KC=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Coffee (Arabica) futures trade on the ICE exchange and represent the premium coffee variety used by specialty roasters worldwide. Brazil and Colombia are the leading Arabica producers, making prices highly sensitive to Brazilian weather conditions, frost events, currency moves, and global consumption trends. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI COFFEE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_coffee"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Cocoa

```{r AGRI COCOA TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/CC=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Cocoa futures trade on ICE and reflect the price of the primary input for chocolate production. Supply is heavily concentrated in West Africa, with Côte d'Ivoire and Ghana accounting for the majority of global production. Prices are driven by West African weather and disease conditions, grinding demand from European and North American chocolate manufacturers, and currency dynamics. Quoted in USD per metric ton, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI COCOA, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_cocoa"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Cotton

```{r AGRI COTTON TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/CT=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Cotton futures (ICE No. 2 contract) track the price of the world's most widely used natural textile fiber. Major producers include the U.S., China, India, Brazil, and Pakistan. Prices are driven by global apparel demand, synthetic fiber competition, planting decisions, and weather conditions in key growing regions. Sensitive to USD strength and Chinese import activity. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI COTTON, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_cotton"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Sugar

```{r AGRI SUGAR TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/SB=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Sugar futures (ICE No. 11 raw sugar contract) represent the global benchmark for raw cane sugar. Brazil is the dominant producer and exporter, and prices are strongly influenced by Brazilian production, the BRL/USD exchange rate, ethanol economics (as sugarcane is an ethanol feedstock), and Indian export policy. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI SUGAR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_sugar"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Live Cattle

```{r AGRI CATTLE TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/LE=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Live Cattle futures (CME front contract) track the price of market-ready cattle prior to slaughter. Prices are sensitive to domestic beef demand, feed costs (corn and hay), herd size cycles, and export demand particularly from Asia. A key indicator of U.S. protein supply chain conditions. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI CATTLE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_live_cattle"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Lean Hogs

```{r AGRI HOGS TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/HE=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Lean Hogs futures (CME front contract) track the price of market-weight hogs used for pork production. Prices are driven by Chinese pork demand (the world's largest pork consumer), U.S. herd dynamics, feed costs, and disease outbreaks such as African Swine Fever. One of the most volatile agricultural contracts given short production cycles and shifting export flows. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI HOGS, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_lean_hogs"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Orange Juice

```{r AGRI OJ TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/OJ=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Orange Juice futures (ICE FCOJ-A contract) track frozen concentrated orange juice, with the U.S. (Florida) and Brazil as the dominant producers. Prices are highly sensitive to Florida frost events, hurricanes, citrus greening disease, and Brazilian crop conditions. One of the most weather-dependent agricultural futures. Quoted in USD per pound, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI OJ, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_orange_juice"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```

### Lumber

```{r AGRI LUMBER TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/quote/LBS=F/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Lumber futures (CME front contract) track the price of random length lumber, a key input for residential construction. Prices are a direct leading indicator of U.S. housing market activity, sensitive to mortgage rates, housing starts, and supply constraints from Canadian sawmill capacity and trade tariffs. One of the most volatile commodity contracts given its tight link to the interest rate cycle. Quoted in USD per thousand board feet, updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r AGRI LUMBER, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(c("fut_lumber"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))
```

```{=html}
</div>
```


