---
title: "Europe Financial and Macro Report"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    theme: flatly
    highlight: kate
    self_contained: true
    css: "/Users/benjaminlachavanne/Desktop/script/finance_analysis/html/style/style.css"


params:
  llm_analysis: false
  
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Main path 
path_main <- file.path("~", "Desktop", "script", "finance_analysis")

# Upload packages, functions and inputs 
source(paste0(path_main,"/initialization/package.R"))         # |Package|
source(paste0(path_main,"/function/function_information.R"))  # |Function price|
source(paste0(path_main,"/function/function_format.R"))       # |Function format|
source(paste0(path_main,"/function/function_visualization.R"))        # |Functions visualization|
source(paste0(path_main,"/function/function_compute.R"))      # |Functions indicator|
source(paste0(path_main,"/function/function_ai.R"))           # |Functions ai|
source(paste0(path_main,"/initialization/input.R"))           # |Input|

# Download all series from the RDS folder
path_rds_folder    <- "/Users/benjaminlachavanne/Desktop/script/finance_analysis/database/rds/"
path_rds_all <- paste0(path_rds_folder,"series_store_all.rds")
series_database <- readRDS(path_rds_all)

# Styled info box
series_info_box <- function(source_html, frequency, adjustment, about) {
  htmltools::HTML(paste0('
  <div class="info-card">
    <div class="info-grid">
      <div class="info-row">
        <span class="info-label">Source</span>
        <span class="info-value">', source_html, '</span>
      </div>
      <div class="info-row">
        <span class="info-label">Frequency</span>
        <span class="info-value">', frequency, '</span>
      </div>
      <div class="info-row">
        <span class="info-label">Adjustment</span>
        <span class="info-value">', adjustment, '</span>
      </div>
    </div>
    <div class="info-about">', about, '</div>
  </div>
  '))
}

# Section label helper
section_label <- function(icon, text) {
  htmltools::HTML(paste0(
    '<div class="section-label"><span class="section-icon">', icon,
    '</span><span class="section-text">', text, '</span></div>'))
}

# Subsection label helper
subsection_label <- function(text) {
  htmltools::HTML(paste0('<div class="subsection-label">', text, '</div>'))
}

# Chart note helper
chart_note <- function(text) {
  htmltools::HTML(paste0('<p class="chart-note">', text, '</p>'))
}
```


<!-- ####################################################################### -->
<!-- Head Title  -->
<!-- ####################################################################### -->

```{=html}
<!-- ── MASTHEAD ─────────────────────────────────────────────────────────────── -->
<div class="masthead">
  <div class="masthead-eyebrow">Macro Research · Europe</div>
  <div class="masthead-title">Europe <span>Financial &amp; Macro Report</span></div>
  <div class="masthead-date">Latest update date: `r format(Sys.Date(), '%B %d, %Y')`</div>
</div>
```


<!-- ####################################################################### -->
<!-- Abstract  -->
<!-- ####################################################################### -->

## Abstract

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Abstract</div>
  </div>
</div>
```

```{=html}
<div class="abstract-box">
<p>This report provides a comprehensive overview of the European economy and financial markets through a structured set of macroeconomic, financial, and market indicators. It covers the European Union (27 countries) and the Euro Area (20 countries), with a country-level breakdown for the main European economies.</p>
<ul>
  <li>The <strong>macroeconomic</strong> section covers the key drivers of economic activity, including output growth, inflation, labor market conditions, household and business behavior, investment, housing, and fiscal balances.</li>
  <li>The <strong>monetary policy</strong> section tracks ECB's stance through interest rates and balance sheet dynamics.</li>
  <li>The <strong>index</strong> and <strong>volatility</strong> sections provide a broad reading of European financial market conditions.</li>
  <li>Finally, <strong>exchange rates</strong> against the euro reflect the international dimension of European financial conditions.</li>
</ul>
<p>Taken together, this report aims to offer a 360° view of the European economic and financial cycle, combining official statistics with market-based signals to support a comprehensive assessment of the current environment.</p>
</div>
```


<!-- ####################################################################### -->
<!-- Macro  -->
<!-- ####################################################################### -->

## Macro

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Macro</div>
  </div>
</div>
```

### Real GDP

```{r EU GDP TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/cache/metadata/en/namq_10_gdp_esms.htm" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Seasonally Adjusted",
  about = "Eurostat reports GDP at market prices under the national accounts item B1GQ, consistent with the ESA 2010 definition, where GDP equals gross value added (B.1G) plus taxes less subsidies on products (D.21 − D.31). Real GDP is measured using chain-linked volume indicators: <code>CLV20_MEUR</code>, which expresses GDP in chain-linked volumes with 2020 as the reference year (million euros), and <code>CLV_PCH_ANN</code>, which represents the annual percentage change of chain-linked volumes, capturing real GDP growth net of inflation effects.")
```

```{=html}
<div class="perf-section">
```

```{r EU GDP, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_rgdp_pc1_es","ea21_rgdp_pc1_es","de_rgdp_pc1_es","fr_rgdp_pc1_es", "it_rgdp_pc1_es", "es_rgdp_pc1_es", "pt_rgdp_pc1_es", "at_rgdp_pc1_es", "nl_rgdp_pc1_es", "dk_rgdp_pc1_es", "no_rgdp_pc1_es", "se_rgdp_pc1_es", "pl_rgdp_pc1_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, REAL GROSS DOMESTIC PRODUCT, Percent Change from Year Ago, Seasonally Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Inflation

```{r EU HICP TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/databrowser/view/PRC_HICP_MANR__custom_3761882/bookmark/table?lang=en&bookmarkId=4ad27e6f-358a-4a3d-82a0-587d69a833eb&c=1667558907980" target="_blank">link</a>',
  frequency = "Monthly",
  adjustment = "Not Adjusted",
  about = "Inflation measured by the Harmonised Index of Consumer Prices (HICP) reflects the change over time in the prices paid by households for a representative basket of goods and services. The HICP is compiled using a common methodology across European countries to ensure cross-country comparability. In the <code>PRC_HICP_MANR</code> dataset, inflation is expressed as the annual rate of change. This indicator is widely used to assess price stability and serves as the reference measure for monetary policy in the euro area.")
```

```{=html}
<div class="perf-section">
```

```{r EU HICP, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_hicp_pc1_es","ea20_hicp_pc1_es","de_hicp_pc1_es","fr_hicp_pc1_es", "it_hicp_pc1_es", "es_hicp_pc1_es", "pt_hicp_pc1_es", "at_hicp_pc1_es", "nl_hicp_pc1_es", "dk_hicp_pc1_es", "no_hicp_pc1_es", "se_hicp_pc1_es", "pl_hicp_pc1_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Harmonised Index of Consumer Prices, Percent Change from Year Ago, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA20 = Euro Area (20 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Unemployment

```{r EU UNEMP TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/databrowser/bookmark/2feeff57-57c9-4278-a50b-7e2279d699c2?lang=en" target="_blank">link</a>',
  frequency = "Monthly",
  adjustment = "Not Adjusted",
  about = "The unemployment rate measures the share of the labour force that is without work, actively seeking employment, and available to start working. It is calculated according to the International Labour Organization (ILO) definition to ensure international comparability. Expressed as a percentage of the total labour force, the indicator provides a key measure of labour market conditions and economic slack. It is widely used to assess the health of the economy and to inform economic and monetary policy decisions.")
```

```{=html}
<div class="perf-section">
```

```{r EU UNEMP, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_unemp_es","ea21_unemp_es","de_unemp_es","fr_unemp_es", "it_unemp_es", "es_unemp_es", "pt_unemp_es", "at_unemp_es", "nl_unemp_es", "dk_unemp_es", "no_unemp_es", "se_unemp_es", "pl_unemp_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Unemployment Rate, Percent of Active Population, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Real Total Consumption

```{r EU RTC TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/cache/metadata/en/namq_10_gdp_esms.htm" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Seasonally and Calendar Adjusted",
  about = "Real total consumption measures the volume of goods and services purchased by households, adjusted for price changes to reflect real purchasing power rather than nominal expenditure. It is compiled according to national accounts standards to ensure cross-country comparability. Expressed in chain-linked volumes <code>CLV_PCH_ANN</code>, it removes the effects of inflation over time, while annual percentage changes capture the real growth rate of consumption. The indicator provides a key measure of domestic demand and is widely used to assess economic momentum and overall business cycle conditions.")
```

```{=html}
<div class="perf-section">
```

```{r EU RTC, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_rtc_pc1_sca_es","ea21_rtc_pc1_es","de_rtc_pc1_es","fr_rtc_pc1_es", "it_rtc_pc1_es", "es_rtc_pc1_es", "pt_rtc_pc1_es", "at_rtc_pc1_es", "nl_rtc_pc1_es", "dk_rtc_pc1_es", "no_rtc_pc1_es", "se_rtc_pc1_es", "pl_rtc_pc1_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Real Total Consumption, Percent Change from Year Ago, Seasonally and Calendar Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Real Household Consumption

```{r EU RHC TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/cache/metadata/en/namq_10_gdp_esms.htm" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Seasonally and Calendar Adjusted",
  about = "Real total consumption <code>P31_S14</code> refers to household final consumption expenditure as defined in the European System of Accounts (ESA 2010). It measures the value of goods and services purchased by households for the direct satisfaction of individual needs. In this dataset, the series is expressed in chain-linked volumes with 2020 as the reference year <code>CLV20_MEUR</code>, meaning values are reported in million euros and adjusted for price changes to reflect real purchasing power over time. This indicator provides a key measure of domestic demand and is an essential component of overall GDP dynamics.")
```

```{=html}
<div class="perf-section">
```

```{r EU RHC TOT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_rfhc_sca_es","ea21_rfhc_sca_es","de_rfhc_sca_es","fr_rfhc_sca_es", "it_rfhc_sca_es", "es_rfhc_sca_es", "pt_rfhc_sca_es", "at_rfhc_sca_es", "nl_rfhc_sca_es", "dk_rfhc_sca_es", "no_rfhc_sca_es", "se_rfhc_sca_es", "pl_rfhc_sca_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Real Household Consumption, Millions of Chained 2020 Euros, Seasonally and Calendar Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

```{=html}
<div class="perf-section">
```

```{r EU RHC PCY, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_rfhc_sca_es","ea21_rfhc_sca_es","de_rfhc_sca_es","fr_rfhc_sca_es", "it_rfhc_sca_es", "es_rfhc_sca_es", "pt_rfhc_sca_es", "at_rfhc_sca_es", "nl_rfhc_sca_es", "dk_rfhc_sca_es", "no_rfhc_sca_es", "se_rfhc_sca_es", "pl_rfhc_sca_es"))

# Compute Percent change from a Year ago
data <- data %>% 
  ts_pcy()

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Real Household Consumption, Percent Change from Year Ago, Seasonally and Calendar Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Real Investment

```{r EU RI TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/cache/metadata/en/namq_10_gdp_esms.htm" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Seasonally and Calendar Adjusted",
  about = "Real gross fixed capital formation <code>P51G</code> refers to investment in fixed assets as defined in the European System of Accounts (ESA 2010). It measures the value of acquisitions less disposals of fixed assets by resident producers, including machinery, equipment, construction, and intellectual property products. In this dataset, the series is expressed in chain-linked volumes with 2020 as the reference year <code>CLV20_MEUR</code>, meaning values are reported in million euros and adjusted for price changes to reflect real investment over time. This indicator provides a key measure of capital accumulation and productive capacity, and is an essential component of overall GDP dynamics.")
```

```{=html}
<div class="perf-section">
```

```{r EU RI TOT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_ri_sca_es","ea21_ri_sca_es","de_ri_sca_es","fr_ri_sca_es", "it_ri_sca_es", "es_ri_sca_es", "pt_ri_sca_es", "at_ri_sca_es", "nl_ri_sca_es", "dk_ri_sca_es", "no_ri_sca_es", "se_ri_sca_es", "pl_ri_sca_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Real Investment, Millions of Chained 2020 Euros, Seasonally and Calendar Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

```{=html}
<div class="perf-section">
```

```{r EU RI PCY, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_ri_sca_es","ea21_ri_sca_es","de_ri_sca_es","fr_ri_sca_es", "it_ri_sca_es", "es_ri_sca_es", "pt_ri_sca_es", "at_ri_sca_es", "nl_ri_sca_es", "dk_ri_sca_es", "no_ri_sca_es", "se_ri_sca_es", "pl_ri_sca_es"))

# Compute Percent change from a Year ago
data <- data %>% 
  ts_pcy()

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Real Investment, Percent Change from Year Ago, Seasonally and Calendar Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Household Savings

```{r EU HS TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/databrowser/view/nasq_10_ki/default/table?lang=en" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Not Adjusted",
  about = "Household saving rate <code>SRG_S14_S15</code> refers to the net saving of households and non-profit institutions serving households (NPISH) as a percentage of their gross disposable income, as defined in the European System of Accounts (ESA 2010). It measures the share of income that is not used for final consumption expenditure and is therefore available for investment or debt reduction. In this dataset, the series is expressed as a percentage, providing a direct measure of households’ saving behaviour over time. This indicator is widely used to assess financial resilience, consumption prospects, and broader macroeconomic dynamics.")
```

```{=html}
<div class="perf-section">
```

```{r EU HS, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_hs_nsa_es","ea20_hs_nsa_es","de_hs_nsa_es","fr_hs_nsa_es", "it_hs_nsa_es", "es_hs_nsa_es", "pt_hs_nsa_es", "at_hs_nsa_es", "nl_hs_nsa_es", "dk_hs_nsa_es", "no_hs_nsa_es", "se_hs_nsa_es", "pl_hs_nsa_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Household Savings, Percentage of gross disposable income, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA20 = Euro Area (20 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Business Investment

```{r EU BI TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/databrowser/view/nasq_10_ki/default/table?lang=en" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Not Adjusted",
  about = "Investment rate of non-financial corporations <code>IRG_S11</code> refers to the gross fixed capital formation of the non-financial corporate sector (S11) expressed as a percentage of its gross value added, as defined in the European System of Accounts (ESA 2010). It measures the share of value added that is devoted to investment in fixed assets such as machinery, equipment, buildings, and intellectual property products. The indicator is therefore expressed as a percentage of gross value added. It provides a key measure of corporate investment behaviour and is widely used to assess productive capacity, business confidence, and medium-term growth prospects.")
```

```{=html}
<div class="perf-section">
```

```{r EU BI, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_bi_nsa_es","ea20_bi_nsa_es","de_bi_nsa_es","fr_bi_nsa_es", "it_bi_nsa_es", "es_bi_nsa_es", "pt_bi_nsa_es", "at_bi_nsa_es", "nl_bi_nsa_es", "dk_bi_nsa_es", "no_bi_nsa_es", "se_bi_nsa_es", "pl_bi_nsa_es"))


# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Business Investment, Percentage of gross fixed capital, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA20 = Euro Area (20 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))
```

```{=html}
</div>
```

### Governement Surplus/Deficit

```{r EU GOVS TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/databrowser/view/gov_10q_ggnfa/default/table?lang=en" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Not Adjusted",
  about = "General government net lending / net borrowing <code>B9</code> (sector <code>S13</code>) refers to the fiscal balance of the general government sector as defined in the European System of Accounts (ESA 2010). It measures the difference between total government revenues and total expenditures over a given period. A positive value indicates a surplus (net lending), while a negative value indicates a deficit (net borrowing).The series are expressed either in million euros <code>MIO_EUR</code>, reflecting the nominal fiscal balance, or as a percentage of GDP <code>PC_GDP</code>, allowing for cross-country comparability and assessment relative to the size of the economy. This indicator is a key measure of fiscal performance and is widely used to monitor public finances, fiscal sustainability, and compliance with European fiscal rules.")
```

```{=html}
<div class="perf-section">
```

```{r EU GOVS PRC, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_govdfsu_nsa_pg_es","ea21_govdfsu_nsa_pg_es","de_govdfsu_nsa_pg_es","fr_govdfsu_nsa_pg_es", "it_govdfsu_nsa_pg_es", "es_govdfsu_nsa_pg_es", "pt_govdfsu_nsa_pg_es", "at_govdfsu_nsa_pg_es", "nl_govdfsu_nsa_pg_es", "dk_govdfsu_nsa_pg_es", "no_govdfsu_nsa_pg_es", "se_govdfsu_nsa_pg_es", "pl_govdfsu_nsa_pg_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Governement Surplus/Deficit, Percentage of GDP, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

```{=html}
<div class="perf-section">
```

```{r EU GOVS TOT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_govdfsu_nsa_es","ea21_govdfsu_nsa_es","de_govdfsu_nsa_es","fr_govdfsu_nsa_es", "it_govdfsu_nsa_es", "es_govdfsu_nsa_es", "pt_govdfsu_nsa_es", "at_govdfsu_nsa_es", "nl_govdfsu_nsa_es", "dk_govdfsu_nsa_es", "no_govdfsu_nsa_es", "se_govdfsu_nsa_es", "pl_govdfsu_nsa_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Governement Surplus/Deficit, Millions Euros, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Governement Debt 

```{r EU GOVD TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/databrowser/view/gov_10q_ggdebt/default/table?lang=en" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Not Adjusted",
  about = "General government gross debt (sector <code>S13</code>) refers to the consolidated stock of liabilities of the general government sector, as defined in the European System of Accounts (ESA 2010). It includes currency and deposits, debt securities, and loans outstanding at the end of the reference period. The indicator is compiled according to the Maastricht definition of government debt, ensuring consistency and comparability across European countries. In this dataset (<code>gov_10q_ggdebt</code>), the series are expressed either in million euros <code>MIO_EUR</code>, reflecting the nominal level of public debt, or as a percentage of GDP <code>PC_GDP</code>, allowing the debt burden to be assessed relative to the size of the economy. This indicator is widely used to evaluate fiscal sustainability, sovereign risk, and compliance with European fiscal rules.")
```

```{=html}
<div class="perf-section">
```

```{r EU GOVD PRC, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_govde_nsa_pg_es","ea21_govde_nsa_pg_es","de_govde_nsa_pg_es","fr_govde_nsa_pg_es", "it_govde_nsa_pg_es", "es_govde_nsa_pg_es", "pt_govde_nsa_pg_es", "at_govde_nsa_pg_es", "nl_govde_nsa_pg_es", "dk_govde_nsa_pg_es", "no_govde_nsa_pg_es", "se_govde_nsa_pg_es", "pl_govde_nsa_pg_es"))


# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Governement Debt, Percentage of GDP, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

```{=html}
<div class="perf-section">
```

```{r EU GOVD TOT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_govde_nsa_es","ea20_govde_nsa_es","de_govde_nsa_es","fr_govde_nsa_es", "it_govde_nsa_es", "es_govde_nsa_es", "pt_govde_nsa_es", "at_govde_nsa_es", "nl_govde_nsa_es", "dk_govde_nsa_es", "no_govde_nsa_es", "se_govde_nsa_es", "pl_govde_nsa_es"))


# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Governement Debt , Millions Euros, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA20 = Euro Area (20 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

```{=html}
<div class="perf-section">
```

```{r EU GOVD PCY, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_govde_nsa_es","ea20_govde_nsa_es","de_govde_nsa_es","fr_govde_nsa_es", "it_govde_nsa_es", "es_govde_nsa_es", "pt_govde_nsa_es", "at_govde_nsa_es", "nl_govde_nsa_es", "dk_govde_nsa_es", "no_govde_nsa_es", "se_govde_nsa_es", "pl_govde_nsa_es"))

# Compute Percent change from a Year ago
data <- data %>% 
  ts_pcy()

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Governement Debt , Percent Change from Year Ago, Not Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA20 = Euro Area (20 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### Housing Prices

```{r EU HP TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Eurostat — <a href="https://ec.europa.eu/eurostat/databrowser/view/prc_hpi_q/default/table?lang=en" target="_blank">link</a>',
  frequency = "Quarterly",
  adjustment = "Not Adjusted",
  about = "House Price Index (HPI) <code>prc_hpi_q</code> measures the change over time in the transaction prices of residential properties purchased by households. It covers both new and existing dwellings and is compiled according to a harmonised methodology to ensure comparability across European countries. In this dataset, the series is expressed as an annual rate of change <code>RCH_A</code>, meaning it reflects the percentage change in house prices compared with the same quarter of the previous year. This indicator provides a key measure of developments in residential property markets and is widely used to assess housing market dynamics, wealth effects, and potential macroeconomic imbalances.")
```

```{=html}
<div class="perf-section">
```

```{r EU HP PRC, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eu27_hp_pc1_es","ea21_hp_pc1_es","de_hp_pc1_es","fr_hp_pc1_es", "it_hp_pc1_es", "es_hp_pc1_es", "pt_hp_pc1_es", "at_hp_pc1_es", "nl_hp_pc1_es", "dk_hp_pc1_es", "no_hp_pc1_es", "se_hp_pc1_es", "pl_hp_pc1_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Union and Euro Zone, Housing prices, Percent Change from Year Ago, Seasonally and Calendar Adjusted"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU27 = European Union (27 countries), EA21 = Euro Area (21 countries), DE = Germany, FR = France, IT = Italy, ES = Spain, PT = Portugal, AT = Austria, NL = Netherlands, DK = Denmark, NO = Norway, SE = Sweden, PL = Poland</em></small>"))

```

```{=html}
</div>
```

### KOF Forecast

```{r EU KOF FOR TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'KOF Nowcasting Lab — <a href="https://nowcastinglab.org/map" target="_blank">link</a>',
  frequency  = "Daily",
  adjustment = "Seasonally Adjusted",
  about = "KOF Nowcasting Lab provides continuously updated real-time estimates of current-quarter and next-quarter real GDP growth for a range of economies including Switzerland, the euro area, Germany, France, Italy, Spain, the United Kingdom, and several others, developed by the KOF Swiss Economic Institute at ETH Zurich. The platform is fully automated with no human judgmental input, updating estimates up to three times daily as new data releases enter the system. It combines four classes of mixed-frequency econometric models fed with approximately 250 daily and monthly macroeconomic and financial series, with individual model forecasts pooled using forecast combination techniques and weaker predictors filtered via elastic net regularization. The core premise is that high-frequency indicators such as business surveys, trade statistics, and financial data are published weeks ahead of the official quarterly GDP release, which arrives with a lag of six to eight weeks after quarter-end in most economies, allowing the models to progressively refine estimates as the information set expands throughout the quarter. The website displays uncertainty bands, individual model outputs, the contribution of each release to forecast revisions, and historical forecast errors.")

```

#### *France*

```{=html}
<div class="perf-section">
```

```{r FR KOF FOR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_kof_nowcast(id = c("FRGDPNC"), last_quarter = 2) %>% 
  rename(date = publication_date, quarter_forecast = date) %>% 
  mutate(name = paste0(name," ",target_period), id = paste0(id,"_",target_period))

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE,title = paste0("KOF Nowcast for France in ", paste0(unique(data$target_period), collapse = " / "), ", Percent Change from Previous Period, Seasonally Adjusted"))),
  div(style = "text-align: center;",
      HTML("<small><em>Note : The x-axis represents the forecast's date of publication for a specific quarter</em></small>")))

```

```{=html}
</div>
```

#### *Germany*

```{=html}
<div class="perf-section">
```

```{r GE KOF FOR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_kof_nowcast(id = c("DEGDPNC"), last_quarter = 2) %>% 
  rename(date = publication_date, quarter_forecast = date) %>% 
  mutate(name = paste0(name," ",target_period), id = paste0(id,"_",target_period))

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE,title = paste0("KOF Nowcast for Germany in ", paste0(unique(data$target_period), collapse = " / "), ", Percent Change from Previous Period, Seasonally Adjusted"))),
  div(style = "text-align: center;",
      HTML("<small><em>Note : The x-axis represents the forecast's date of publication for a specific quarter</em></small>")))

```

```{=html}
</div>
```

#### *Spain*

```{=html}
<div class="perf-section">
```

```{r SP KOF FOR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_kof_nowcast(id = c("ESGDPNC"), last_quarter = 2) %>% 
  rename(date = publication_date, quarter_forecast = date) %>% 
  mutate(name = paste0(name," ",target_period), id = paste0(id,"_",target_period))

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE,title = paste0("KOF Nowcast for Spain in ", paste0(unique(data$target_period), collapse = " / "), ", Percent Change from Previous Period, Seasonally Adjusted"))),
  div(style = "text-align: center;",
      HTML("<small><em>Note : The x-axis represents the forecast's date of publication for a specific quarter</em></small>")))

```

```{=html}
</div>
```

#### *Italy*

```{=html}
<div class="perf-section">
```

```{r EU KOF FOR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_kof_nowcast(id = c("ITGDPNC"), last_quarter = 2) %>% 
  rename(date = publication_date, quarter_forecast = date) %>% 
  mutate(name = paste0(name," ",target_period), id = paste0(id,"_",target_period))

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE,title = paste0("KOF Nowcast for Italy in ", paste0(unique(data$target_period), collapse = " / "), ", Percent Change from Previous Period, Seasonally Adjusted"))),
  div(style = "text-align: center;",
      HTML("<small><em>Note : The x-axis represents the forecast's date of publication for a specific quarter</em></small>")))

```

```{=html}
</div>
```

#### *Euro Zone*

```{=html}
<div class="perf-section">
```

```{r EA KOF FOR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_kof_nowcast(id = c("EA_AGGGDPNC"), last_quarter = 2) %>% 
  rename(date = publication_date, quarter_forecast = date) %>% 
  mutate(name = paste0(name," ",target_period), id = paste0(id,"_",target_period))

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE,title = paste0("KOF Nowcast for Euro Area in ", paste0(unique(data$target_period), collapse = " / "), ", Percent Change from Previous Period, Seasonally Adjusted"))),
  div(style = "text-align: center;",
      HTML("<small><em>Note : The x-axis represents the forecast's date of publication for a specific quarter</em></small>")))

```

```{=html}
</div>
```

<!-- ####################################################################### -->
<!-- ECB  -->
<!-- ####################################################################### -->

## Monetary Policy

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Monetary Policy</div>
  </div>
</div>
```

### ECB & Euribor Rates

```{r ECB RATE TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'FRED — <a href="https://fred.stlouisfed.org/" target="_blank">link</a>  and EURIBOR — <a href="https://www.euribor-rates.eu/en/euribor-charts/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = paste0(
  '1) <b> ECB Main Refinancing Operations Rate — <a href="https://fred.stlouisfed.org/series/ECBMRRFR" target="_blank">	ECBMRRFR</a></b>. ',
  'ECB Main Refinancing Operations Rate: Fixed Rate Tenders for Euro Area measures the interest rate at which the European Central Bank provides the bulk of liquidity to the euro area banking system through its main refinancing operations, published by the European Central Bank from its Key ECB Interest Rates release. Main refinancing operations are weekly open market transactions through which the ECB lends funds to eligible counterparty banks against adequate collateral for a one-week maturity, with the fixed rate serving as the floor for the cost of short-term borrowing in the euro area interbank market. Changes to the MRO rate are decided by the ECB Governing Council at its monetary policy meetings and transmit to the broader economy through their influence on bank lending rates, mortgage rates, corporate borrowing costs, and asset prices across the euro area. Data reflect the changing composition of the euro area over time. Released daily on a 7-day basis.',
  '<br><br>',
  '2) <b>ECB Deposit Facility Rate — <a href="https://fred.stlouisfed.org/series/ECBDFR" target="_blank">ECBDFR</a></b>. ',
  'ECB Deposit Facility Rate for Euro Area measures the interest rate at which eligible counterparty banks may make overnight deposits with the Eurosystem, published by the European Central Bank from its Key ECB Interest Rates release. It forms the lower bound of the ECB\'s interest rate corridor, the rate at which excess liquidity parked overnight at the central bank is remunerated. In periods of abundant excess reserves in the banking system, such as following large-scale asset purchase programs, the deposit facility rate effectively becomes the operative policy rate driving short-term money market rates and the euro short-term rate (€STR), as the marginal cost of funds in the interbank market is anchored to the rate banks can earn by depositing overnight at the ECB rather than lending to peers. Between June 2014 and September 2022, the rate was held in negative territory as part of the ECB\'s unconventional monetary policy toolkit, penalizing banks for holding excess reserves with the aim of incentivizing lending to the real economy. Changes to the deposit facility rate are decided by the ECB Governing Council at its monetary policy meetings and transmit to borrowing costs, credit conditions, and asset prices across the euro area. Data reflect the changing composition of the euro area over time. Released daily on a 7-day basis.',
  '<br><br>',
  '3) <b>ECB Marginal Lending Facility Rate — <a href="https://fred.stlouisfed.org/series/ECBMLFR" target="_blank">ECBMLFR</a></b>. ',
  'ECB Marginal Lending Facility Rate for Euro Area measures the interest rate at which eligible counterparty banks may obtain overnight credit from the Eurosystem against adequate collateral, published by the European Central Bank from its Key ECB Interest Rates release. It forms the upper bound of the ECB\'s interest rate corridor, the ceiling beyond which short-term interbank borrowing rates cannot rise, as any bank in need of overnight liquidity can always obtain it from the Eurosystem at this rate rather than paying more in the open market. Access to the marginal lending facility is available on demand to eligible counterparties, making it a backstop liquidity instrument of last resort for banks facing short-term funding shortfalls at the end of the business day. Because it sets the hard ceiling on overnight money market rates, the spread between the marginal lending facility rate and the deposit facility rate defines the width of the ECB\'s policy corridor, which the Governing Council has periodically adjusted to influence money market volatility and the transmission of monetary policy. Changes to the rate are decided by the ECB Governing Council at its monetary policy meetings. Data reflect the changing composition of the euro area over time. Released daily on a 7-day basis.',
  '<br><br>',
      '4) <b>Euribor 1 week — <a href="https://www.euribor-rates.eu/en/euribor-rates-by-year/" target="_blank">EURIBOR1W</a></b>. ',
  'Euro Interbank Offered Rate 1-Week measures the average interest rate at which a panel of leading European banks are willing to lend unsecured funds to one another in the euro interbank market for a one-week maturity, administered by the European Money Markets Institute (EMMI) and calculated daily on each TARGET2 business day. It is derived from the trimmed average of rate submissions from a panel of representative banks after excluding the highest and lowest 15% of contributions. As an unsecured interbank lending rate, EURIBOR reflects the marginal cost of short-term euro-denominated funding in the wholesale money market and is directly anchored to ECB monetary policy expectations, with the 1-week tenor sitting at the very short end of the euro yield curve and tracking closely the ECB deposit facility rate and overnight €STR fixings. It serves as a reference rate for a broad range of financial instruments including floating-rate loans, interest rate swaps, and money market products, and is widely used as a benchmark for short-term euro funding conditions across the euro area banking system. Published daily.',
  '<br><br>',
    '5) <b>Euribor 1 month — <a href="https://www.euribor-rates.eu/en/euribor-rates-by-year/" target="_blank">EURIBOR1M</a></b>. ',
  'Euro Interbank Offered Rate 1-Month measures the average interest rate at which a panel of leading European banks are willing to lend unsecured funds to one another in the euro interbank market for a one-month maturity, administered by the European Money Markets Institute (EMMI) and calculated daily on each TARGET2 business day. It is derived from the trimmed average of rate submissions from a panel of representative banks after excluding the highest and lowest 15% of contributions. Sitting between the very short end of the euro yield curve represented by the 1-week tenor and the more widely referenced 3-month tenor, EURIBOR 1M captures market expectations of ECB monetary policy over a one-month horizon and is particularly sensitive to near-term central bank rate decisions, short-term liquidity conditions in the euro area banking system, and month-end balance sheet pressures that can temporarily distort interbank funding costs. It serves as a reference rate for floating-rate financial instruments with shorter reset periods than those indexed to the 3-month tenor, including certain floating-rate loans, revolving credit facilities, and short-dated interest rate derivatives, and is also used as a benchmark in money market funds and cash management products requiring a shorter-duration reference rate. Published daily.',
  '<br><br>',
    '6) <b>Euribor 3 months — <a href="https://www.euribor-rates.eu/en/euribor-rates-by-year/" target="_blank">EURIBOR3M</a></b>. ',
  'Euro Interbank Offered Rate 3-Month measures the average interest rate at which a panel of leading European banks are willing to lend unsecured funds to one another in the euro interbank market for a three-month maturity, administered by the European Money Markets Institute (EMMI) and calculated daily on each TARGET2 business day. It is the most widely referenced EURIBOR tenor and is derived from the trimmed average of rate submissions from a panel of representative banks after excluding the highest and lowest 15% of contributions. As the benchmark rate for three-month unsecured euro funding, EURIBOR 3M occupies a central position in the euro area\'s short-term interest rate complex, more forward-looking than the overnight €STR or the 1-week tenor, it embeds market expectations of ECB monetary policy over a three-month horizon and therefore responds to shifts in rate expectations, central bank communication, and broader credit and liquidity conditions in the euro area banking system. It serves as the primary reference rate for a vast range of financial contracts including floating-rate mortgages and corporate loans, interest rate swaps, futures contracts traded on Euronext Amsterdam (formerly LIFFE), and other derivatives instruments, making it one of the most systemically important benchmark rates in global fixed income markets. Published daily.',
  '<br><br>',
    '7) <b>Euribor 6 months — <a href="https://www.euribor-rates.eu/en/euribor-rates-by-year/" target="_blank">EURIBOR6M</a></b>. ',
  'Euro Interbank Offered Rate 6-Month measures the average interest rate at which a panel of leading European banks are willing to lend unsecured funds to one another in the euro interbank market for a six-month maturity, administered by the European Money Markets Institute (EMMI) and calculated daily on each TARGET2 business day. It is derived from the trimmed average of rate submissions from a panel of representative banks after excluding the highest and lowest 15% of contributions. As a six-month tenor, EURIBOR 6M embeds market expectations of ECB monetary policy over a longer horizon than the 1-month and 3-month tenors, making it more sensitive to the anticipated trajectory of the policy rate cycle rather than to immediate near-term rate decisions, and incorporating a somewhat larger term premium to compensate lenders for the additional duration and credit risk associated with a longer unsecured lending period. It serves as a widely used reference rate for floating-rate mortgages, particularly in Spain, Italy, and Portugal where retail mortgage contracts have historically been indexed to this tenor, as well as for medium-term corporate loans, interest rate swaps, and other floating-rate financial instruments with semi-annual reset periods. Its prominence in the retail mortgage market of several large euro area economies makes EURIBOR 6M an important transmission channel through which ECB monetary policy decisions pass through to household borrowing costs and real estate affordability. Published daily.',
  '<br><br>',
    '8) <b>Euribor 12 months — <a href="https://www.euribor-rates.eu/en/euribor-rates-by-year/" target="_blank">EURIBOR12M</a></b>. ',
  'Euro Interbank Offered Rate 12-Month measures the average interest rate at which a panel of leading European banks are willing to lend unsecured funds to one another in the euro interbank market for a twelve-month maturity, administered by the European Money Markets Institute (EMMI) and calculated daily on each TARGET2 business day. It is derived from the trimmed average of rate submissions from a panel of representative banks after excluding the highest and lowest 15% of contributions. As the longest standard EURIBOR tenor, EURIBOR 12M sits at the far end of the short-term euro yield curve and incorporates market expectations of ECB monetary policy over a full year, making it the most sensitive of the EURIBOR family to medium-term rate cycle expectations, term premium dynamics, and longer-horizon credit and liquidity risk in the euro area banking system. Because it reflects anticipated funding conditions over twelve months rather than near-term policy decisions, it tends to exhibit smoother dynamics than shorter tenors during periods of rate volatility while being more reactive to shifts in the medium-term monetary policy outlook. It serves as a reference rate for longer reset-period floating-rate instruments including annual-reset mortgages, medium-term corporate credit facilities, and certain interest rate swap and cap structures, and is also used as a benchmark in structured finance and covered bond markets. Its position at the boundary between short-term money market rates and longer-term capital market rates gives it additional significance as an indicator of the overall shape and steepness of the short end of the euro yield curve. Published daily.'))
```

```{=html}
<div class="perf-section">
```

```{r ECB RATE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("ea20_mrr_es","ea20_depfr_es","ea20_mlr_es","ea20_euribor1w", "ea20_euribor1m", "ea20_euribor3m", "ea20_euribor6m", "ea20_euribor12m" ))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "European Short-Term Interest Rates, ECB Short-Term Interest Rate vs. Euribor"))

```

```{=html}
</div>
```

### ECB Total Assets 

```{r ECB ASS TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'FRED — <a href="https://fred.stlouisfed.org/series/ECBASSETSW" target="_blank">link</a>',
  frequency = "Weekly",
  adjustment = "Not Adjusted",
  about = "Central Bank Assets for Euro Area measures the total assets held on the consolidated balance sheet of the Eurosystem, comprising the European Central Bank and the national central banks of all euro area member states, published by the European Central Bank from its Weekly Financial Statements of the Eurosystem. The asset side of the balance sheet encompasses loans to euro area credit institutions (primarily refinancing operations through which liquidity is supplied to the banking system), securities held for monetary policy purposes (including government and corporate bonds acquired under asset purchase programs such as the Asset Purchase Programme and the Pandemic Emergency Purchase Programme), foreign reserve assets, gold holdings, and other financial assets. Rapid expansion of the balance sheet, commonly referred to as quantitative easing, reflects periods of active asset purchases aimed at easing financial conditions and stimulating inflation toward the ECB\'s target, while balance sheet contraction, quantitative tightening, reflects the unwinding of those holdings as policy normalizes. As the broadest available measure of ECB monetary policy accommodation, the size and trajectory of the Eurosystem balance sheet are closely watched as a key indicator of the stance of unconventional monetary policy in the euro area, complementing the signal provided by the three key ECB policy rates. Reported in millions of euros, Not Adjusted, released weekly.")
```

```{=html}
<div class="perf-section">
```

```{r ECB ASS, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "ea20_ecb_total_asset_fd")

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE))

```

```{=html}
</div>
```

<!-- ####################################################################### -->
<!-- Index  -->
<!-- ####################################################################### -->

## Index

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Index</div>
  </div>
</div>
```

### Europe Equity Indices

```{r EU FIN IND TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Yahoo — <a href="https://finance.yahoo.com/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = paste0(
  '1) <b> DAX — <a href="https://finance.yahoo.com/quote/%5EGDAXI/" target="_blank">DAX</a></b>. ',
  'DAX is Germany\'s primary equity benchmark, a performance index tracking the 40 largest and most liquid companies listed on the Frankfurt Stock Exchange, maintained by Qontigo (formerly Deutsche Börse). Unlike most major equity indices which are price-return indices, the DAX is calculated as a total return index by default, meaning dividends and other cash distributions are reinvested into the index, making direct long-run comparisons with price-return indices such as the S&P 500 or FTSE 100 require adjustment. Constituents are selected based on market capitalization and order book volume, and span all major sectors of the German economy including automotive (Volkswagen, BMW, Mercedes-Benz), chemicals and industrials (BASF, Siemens, Linde), financials (Deutsche Bank, Allianz, Munich Re), healthcare (Bayer, Fresenius), and technology (SAP, Infineon). Because Germany is the largest economy in the euro area and one of the world\'s leading export nations, the DAX is sensitive not only to domestic economic conditions but also to global trade dynamics, euro area monetary policy, energy prices, given Germany\'s industrial energy intensity, and demand from key trading partners including China and the United States. Quoted in index points and updated daily with closing prices.',
  '<br><br>',
  '2) <b>CAC 40 — <a href="https://finance.yahoo.com/quote/%5EFCHI/" target="_blank">CAC 40</a></b>. ',
  'CAC 40 is France\'s primary equity benchmark, a free-float market-capitalization-weighted index tracking the 40 largest and most actively traded companies listed on Euronext Paris, maintained by Euronext. Constituents are selected from the top 100 companies by order book turnover on the exchange and reviewed quarterly by an independent steering committee, with weights capped to prevent excessive concentration. The index spans a broad range of sectors including luxury goods and consumer products (LVMH, L\'Oréal, Hermès, Kering), energy (TotalEnergies), industrials (Schneider Electric, Saint-Gobain, Airbus), financials (BNP Paribas, Société Générale, AXA), and healthcare (Sanofi). A defining characteristic of the CAC 40 is its significant international revenue exposure, constituent companies generate the majority of their revenues outside of France, making the index more reflective of global economic conditions and euro strength than of the French domestic economy alone. This heavy international orientation means the CAC 40 is particularly sensitive to global growth momentum, currency movements, Chinese consumer demand (given the weight of luxury goods exporters), and commodity prices. Quoted in index pointsand updated daily with closing prices.',
  '<br><br>',
    '3) <b>OMX — <a href="https://finance.yahoo.com/quote/%5EOMX/" target="_blank">OMX</a></b>. ',
  'OMX Stockholm 30 is Sweden\'s primary equity benchmark, a market-capitalization-weighted index tracking the 30 most actively traded companies listed on Nasdaq Stockholm, maintained by Nasdaq. Constituents are selected based on trading volume over a six-month observation period and reviewed twice yearly, with weights determined by free-float adjusted market capitalization. The index spans key sectors of the Swedish economy including financials (Swedbank, SEB, Handelsbanken, Nordea), industrials and engineering (Atlas Copco, Sandvik, SKF, Volvo, Ericsson), retail and consumer goods (H&M), and healthcare and pharmaceuticals (AstraZeneca). A notable characteristic of the OMX Stockholm 30 is its heavy weighting toward large multinational industrial and financial companies that derive the majority of their revenues internationally, making the index more sensitive to global trade conditions, European monetary policy, and the Swedish krona exchange rate than to Swedish domestic demand alone. Sweden\'s status as a small open economy with a significant manufacturing and engineering export base also makes the index particularly responsive to global industrial cycle dynamics and demand from major trading partners in the euro area and beyond. Quoted in index pointsand updated daily with closing prices.',
  '<br><br>',
  '4) <b>AEX — <a href="https://finance.yahoo.com/quote/%5EAEX/" target="_blank">AEX</a></b>. ',
  'AEX is the Netherlands\' primary equity benchmark, a free-float market-capitalization-weighted index tracking the 25 largest and most actively traded companies listed on Euronext Amsterdam, maintained by Euronext. Constituents are selected based on free-float adjusted market capitalization and trading volume, reviewed annually, with individual weights capped at 15% to limit concentration risk. The index is heavily concentrated in a small number of globally significant companies spanning semiconductors and technology equipment (ASML, the world\'s sole supplier of extreme ultraviolet lithography machines), financials (ING, ABN AMRO), consumer staples and personal care (Unilever), energy (Shell), and professional publishing and information services (RELX, Wolters Kluwer). A defining feature of the AEX is its outsized exposure to the global semiconductor supply chain through ASML, whose weight in the index is typically among the largest of any single constituent in a major European benchmark, making the index unusually sensitive to capital expenditure cycles in the semiconductor industry, export control policy, and technology sector sentiment relative to other European indices. Given that constituent companies generate the vast majority of their revenues internationally, the AEX is more a barometer of global economic conditions, trade flows, and sector-specific dynamics than of the Dutch domestic economy. Quoted in index points and updated daily with closing prices.',
  '<br><br>',
  '5) <b>IBEX — <a href="https://finance.yahoo.com/quote/%5EIBEX/" target="_blank">IBEX</a></b>. ',
  'IBEX 35 is Spain\'s primary equity benchmark, a free-float market-capitalization-weighted index tracking the 35 most liquid companies listed on the Bolsa de Madrid and the Spanish continuous market, maintained by Sociedad de Bolsas and reviewed semi-annually by a technical advisory committee. The index is heavily concentrated in financials (Banco Santander, BBVA, CaixaBank, Sabadell), utilities and infrastructure (Iberdrola, Endesa, Red Eléctrica), telecommunications (Telefónica), and consumer services and retail (Inditex, the parent company of Zara and the world\'s largest fashion retailer by revenue). A defining characteristic of the IBEX 35 is the significant Latin American revenue exposure of its largest constituents, particularly its major banks and Telefónica,  making the index unusually sensitive to economic and political conditions in Brazil, Mexico, and other Latin American markets relative to other major European benchmarks. Domestically, the index is also sensitive to Spanish real estate and construction activity, tourism flows, and the broader health of the Spanish consumer, given the economy\'s historical reliance on these sectors. The large weight of rate-sensitive financial and utility stocks additionally makes the IBEX 35 particularly responsive to changes in European Central Bank monetary policy and euro area sovereign bond yields. Quoted in index points and updated daily with closing prices.',
  '<br><br>',
  '6) <b>FTSEMIB — <a href="https://finance.yahoo.com/quote/FTSEMIB.MI/" target="_blank">FTSEMIB</a></b>. ',
  'FTSE MIB is Italy\'s primary equity benchmark, a free-float market-capitalization-weighted index tracking the 40 largest and most liquid companies listed on Borsa Italiana, now part of Euronext, maintained jointly by FTSE Russell and Borsa Italiana and reviewed quarterly. The index is heavily concentrated in financials (Intesa Sanpaolo, UniCredit, Mediobanca, Generali), energy (ENI, Enel), utilities (A2A, Hera), telecommunications (Telecom Italia), and luxury and consumer goods (Ferrari, Moncler, Campari). A defining structural characteristic of the FTSE MIB is its exceptionally high weighting toward the financial sector, banks and insurance companies collectively represent one of the largest sectoral allocations of any major European benchmark, making the index particularly sensitive to changes in European Central Bank monetary policy, euro area sovereign bond spreads, and the health of the Italian banking system, which has historically carried elevated levels of non-performing loans relative to northern European peers. Because Italian government bonds (BTPs) feature prominently on the balance sheets of domestic banks, the spread between Italian and German ten-year sovereign yields (the BTP-Bund spread) is closely watched as a concurrent risk indicator for the index. The relatively limited presence of global technology and industrial exporters compared to northern European benchmarks makes the FTSE MIB more exposed to Italian and euro area domestic conditions than to global trade dynamics. Quoted in index points and updated daily with closing prices.',
  '<br><br>',
    '7) <b>STOXX 50 — <a href="https://fr.finance.yahoo.com/quote/%5ESTOXX50E/" target="_blank">STOXX50EP</a></b>. ',
  'EURO STOXX 50 is the euro area\'s primary blue-chip equity benchmark, a free-float market-capitalization-weighted index tracking the 50 largest and most liquid companies across the eurozone, maintained by STOXX Ltd. and reviewed annually. Constituents are selected from the EURO STOXX index universe, itself drawn from 11 euro area countries including Germany, France, the Netherlands, Spain, Italy, Belgium, Finland, Ireland, Luxembourg, Austria, and Portugal, and represent the supersector leaders of the eurozone economy, spanning financials (BNP Paribas, Allianz, ING, Santander), technology and semiconductors (ASML, SAP, Infineon), energy (TotalEnergies, Shell), industrials (Siemens, Airbus, Schneider Electric), consumer goods and luxury (LVMH, L\'Oréal, Inditex), and healthcare (Sanofi, Novo Nordisk). As the most widely tracked benchmark for euro area equities, the EURO STOXX 50 is the underlying reference for one of the most liquid derivatives markets in the world, including futures and options traded on Eurex, as well as for a large number of exchange-traded funds and structured products. Unlike the broader STOXX Europe 600, it explicitly excludes non-euro area countries such as the United Kingdom and Switzerland, making it a purer barometer of eurozone economic and monetary policy conditions, particularly ECB interest rate decisions, euro area growth dynamics, and sovereign credit risk. Quoted in index points and updated publish daily with closing prices.',
  '<br><br>',
  '8) <b>STXE 600 — <a href="https://fr.finance.yahoo.com/quote/%5ESTOXX/" target="_blank">STOXX</a></b>. ',
  'STOXX Europe 600 is the broadest pan-European equity benchmark, a free-float market-capitalization-weighted index tracking 600 large, mid, and small-cap companies across 17 European countries, maintained by STOXX Ltd., a subsidiary of Deutsche Börse Group. Unlike the EURO STOXX 50 which is restricted to blue-chip companies of the euro area, the STOXX Europe 600 encompasses both euro area and non-euro area countries including the United Kingdom, Switzerland, Sweden, Norway, and Denmark, providing a more comprehensive representation of the investable European equity universe. Constituents are selected from a broader universe ranked by free-float market capitalization and reviewed quarterly, with coverage spanning all major sectors including financials, healthcare, industrials, consumer goods, technology, energy, and utilities. Because the index includes large non-euro area markets, particularly the United Kingdom and Switzerland, which together represent a significant share of total index weight, it is sensitive not only to ECB monetary policy and euro area economic conditions but also to Bank of England policy, Swiss National Bank decisions, and the currency dynamics of the British pound, Swiss franc, and Swedish krona relative to the euro. The breadth of its geographic and sector coverage makes the STOXX Europe 600 the standard reference benchmark used by pan-European institutional investors and the underlying index for a large number of exchange-traded funds and structured products tracking European equity markets as a whole. Quoted in index points and updated daily with closing prices.'))
```

#### *Table*

```{=html}
<div class="perf-section">
```

```{r FIN IND TABLE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Mapping tickers to readable names
labels <- c(
  "^GDAXI"    = "DAX",
  "^FCHI"     = "CAC 40",
  "^OMX"      = "OMX Stockholm 30",
  "^AEX"      = "AEX",
  "^IBEX"     = "IBEX 35",
  "FTSEMIB.MI"= "FTSE MIB",
  "^STOXX50E" = "Euro Stoxx 50",
  "^STOXX"    = "Stoxx Europe 600"
)

# Get series
indices <- c("^GDAXI", "^FCHI", "^OMX", "^AEX", "^IBEX", "FTSEMIB.MI","^STOXX50E","^STOXX")

# Plot serie
div(style = "display: flex; justify-content: center;",
   produce_performance_table(series = indices, label = labels))
```

```{=html}
</div>
```

#### *DAX*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND DAX, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("dax"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *CAC 40*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND CAC40, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("cac40"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *OMX*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND OMX, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("omx30"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *AEX*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND AEX, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("aex"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *IBEX*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND IBEX, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("ibex35"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *FTSEMIB*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND FTSEMIB, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("ftsemib"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *STOXX 50*

```{=html}
<div class="perf-section">
```

```{r EU FIN STOXX 50, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("eurostoxx"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *STXE 600*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND STXE 600, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("stoxxeur600"))

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

#### *Comparison*

```{=html}
<div class="perf-section">
```

```{r EU FIN IND ALL, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("dax", "cac40", "ftsemib", "ibex35", "aex", "omx30", "stoxxeur600", "eurostoxx"))

# Compute index
data <- compute_rebase(df = data, base_date = "2015-01-07")

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "Europe Equity Indices – Indexed Performance (2015:01:07 = 100)"))

```

```{=html}
</div>
```

### VSTOXX Volatility Index

```{r VSTOXX TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'STOXX — <a href="https://stoxx.com/index/v2tx/" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "EURO STOXX 50 Volatility Index measures the market\'s expectation of near-term to long-term volatility in the EURO STOXX 50, maintained by STOXX Ltd. and calculated in real time from the prices of EURO STOXX 50 options across all available strikes and a range of expiration dates. Methodologically, it is computed as the square root of the implied variance derived from the full cross-section of listed options on the EURO STOXX 50, producing a forward-looking estimate of annualized volatility expressed in percentage points, an approach directly analogous to that used by the CBOE VIX for the S&P 500, making the two indices broadly comparable as measures of equity market fear in their respective regions. Because it is anchored to the EURO STOXX 50, the primary blue-chip benchmark for the euro area, the VSTOXX captures investor uncertainty specifically related to European economic conditions, ECB monetary policy, euro area sovereign risk, and geopolitical developments on the continent. Elevated readings historically correspond to periods of financial stress, political uncertainty, or macroeconomic deterioration within the euro area, while low readings reflect investor complacency and stable conditions. It serves as the underlying reference for VSTOXX futures and options traded on Eurex, making it both a sentiment indicator and an actively tradeable volatility benchmark. Quoted in annualized percentage points, updated daily with closing prices")
```

```{=html}
<div class="perf-section">
```

```{r VSTOXX, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "vstoxx_idx")

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = TRUE))

```

```{=html}
</div>
```

### ZEW Index

```{r ZEW TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'Investing — <a href="https://www.investing.com/economic-calendar/zew-economic-sentiment-310" target="_blank">link</a>',
  frequency = "Daily",
  adjustment = "Not Adjusted",
  about = "Eurozone ZEW Economic Sentiment Index measures the six-month economic outlook for the euro area among financial market experts, published monthly by the Zentrum für Europäische Wirtschaftsforschung (ZEW — Centre for European Economic Research) in Mannheim, Germany. It is derived from a survey of approximately 350 German institutional investors and analysts who assess whether they expect euro area economic conditions to improve, remain unchanged, or deteriorate over the following six months, with the index calculated as the net balance between the share of optimistic and pessimistic respondents. A reading above zero indicates that optimists outnumber pessimists and signals positive near-term growth expectations for the euro area, while a reading below zero reflects a majority expecting deterioration. Because the survey captures the forward-looking expectations of sophisticated financial market participants rather than current business conditions, it serves as a leading indicator of euro area economic activity, with shifts in the index historically anticipating turning points in euro area GDP growth by several months. Updated daily with closing prices.")
```

```{=html}
<div class="perf-section">
```

```{r ZEW, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "zwe_idx_inv")


# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE))

```

```{=html}
</div>
```

### Economic Policy Index

```{r EPU TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'EPU — <a href="https://www.policyuncertainty.com/us_monthly.html" target="_blank">link</a>',
  frequency = "Monthly",
  adjustment = "Not Adjusted",
  about = "Economic Policy Uncertainty Indices for Europe, Germany, France, Italy and Spain measure the degree of uncertainty surrounding economic policy across multiple countries and global aggregates, developed by Baker, Bloom, and Davis. Each national index is constructed by combining three components: the frequency of newspaper articles mentioning economic uncertainty and policy-related terms, the number of federal tax code provisions set to expire in coming years, and the dispersion of economic forecasts among professional forecasters, with the relative weighting of components varying by country based on data availability. Elevated readings signal heightened uncertainty about the direction of fiscal, regulatory, monetary, or trade policy, which tends to suppress business investment, hiring, and consumer spending as firms and households delay decisions pending greater clarity, making the indices useful coincident-to-leading indicators of economic activity slowdowns and financial market volatility. All series are reported as diffusion indices normalized to a long-run mean of 100, not seasonally adjusted, released monthly.")
```

```{=html}
<div class="perf-section">
```

```{r EPU, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = c("de_epu", "fr_epu", "eu_epu", "es_epu", "it_epu"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = FALSE, title = "Economic Policy Uncertainty Index for Germany, France, Spain, Italy and Europe"))
div(style = "text-align: center;",
    HTML("<small><em>Note : EU = European Union (27 countries), DE = Germany, FR = France, IT = Italy, ES = Spain </em></small>"))
```

```{=html}
</div>
```

<!-- ####################################################################### -->
<!-- Indicator  -->
<!-- ####################################################################### -->

## Indicator

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Indicator</div>
  </div>
</div>
```

### KOF Economic Sentiment

```{r KOF ES TXT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = 'KOF — <a href="https://kof.ethz.ch/fr/previsions-indicateurs/indicateurs/kof-indice-climat-economique.html" target="_blank">link</a>',
  frequency = "Monthly",
  adjustment = "Seasonally Adjusted",
  about = "KOF Economic Sentiment Indicator measures the overall economic sentiment in Switzerland, published by the KOF Swiss Economic Institute at ETH Zurich from its business tendency surveys and from consumer surveys conducted by the State Secretariat for Economic Affairs (SECO). It is constructed using the methodology of the European Commission, the same framework applied to all EU member states and euro area aggregates, making it directly comparable to the Economic Sentiment Indicator published for the European Union and the euro area, and thereby allowing Swiss business cycle dynamics to be assessed against those of Switzerland\'s main trading partners on a consistent methodological basis. The composite is assembled from sector-level confidence indicators derived from individual survey responses across five components, weighted as follows: manufacturing (40%), other services (30%), consumer confidence as measured by SECO surveys (20%), construction (5%), and retail trade (5%). The dominant weight assigned to manufacturing reflects its central role in Swiss export activity and GDP, while the inclusion of consumer confidence introduces a demand-side dimension alongside the supply-side business survey components. Reported as a composite index, released monthly.")
```

```{=html}
<div class="perf-section">
```

```{r KOF ES, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
# Get series
data <- get_series(name = c("kof_ind_ch_es", "kof_ind_eu_es"))

# Plot serie
div(style = "display: flex; justify-content: center;",
    produce_interactive_plot(df = data, sma = TRUE, title = "KOF ECONOMIC SENTIMENT INDICATOR For switzerland and Europe"))
```

```{=html}
</div>
```

<!-- ####################################################################### -->
<!-- Exchange Rates  -->
<!-- ####################################################################### -->

## Exchange Rates

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Exchange Rates</div>
  </div>
</div>
```

### USD/EUR

```{=html}
<div class="perf-section">
```

```{r USDEUR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "eur_usd")

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

### GBP/EUR

```{=html}
<div class="perf-section">
```

```{r GBPEUR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "gbp_eur")

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

### CHF/EUR

```{=html}
<div class="perf-section">
```

```{r CHFEUR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "chf_eur")

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

### CAD/EUR

```{=html}
<div class="perf-section">
```

```{r CADEUR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "cad_eur")

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```

### JPY/EUR

```{=html}
<div class="perf-section">
```

```{r JPYEUR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

# Get series
data <- get_series(name = "jpy_eur")

# Compute sma 
data <- compute_moving_average(df = data, date_col = "date", value_col = "value")

# Plot serie
tagList(
  div(style = "display: flex; justify-content: center;",
      produce_interactive_plot(df = data, sma = TRUE)),
  div(style = "text-align: center;",
      HTML("<small><em>Note : Simple Moving Averages are computed with the last 20, 50 and 200 closing prices</em></small>")))

```

```{=html}
</div>
```
