---
title: "Custom Ticker Analysis"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    theme: flatly
    highlight: kate
    self_contained: true
    css: "style.css"   # chemin relatif → copié dans output_dir par le workflow

params:
  ticker:       "AAPL"   # valeur par défaut pour les tests locaux
  llm_analysis: false
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# ── Path principal : local ou CI ──────────────────────────────────────────────
if (Sys.getenv("CI") == "true") {
  path_main <- file.path(getwd(), "finance_analysis")
} else {
  path_main <- file.path("~", "Desktop", "script", "finance_analysis")
}

# ── Ticker (depuis params) ────────────────────────────────────────────────────
ticker <- toupper(trimws(params$ticker))

# ── Packages & fonctions ──────────────────────────────────────────────────────
source(paste0(path_main, "/initialization/package.R"))
source(paste0(path_main, "/function/function_information.R"))
source(paste0(path_main, "/function/function_format.R"))
source(paste0(path_main, "/function/function_visualization.R"))
source(paste0(path_main, "/function/function_compute.R"))
source(paste0(path_main, "/function/function_ai.R"))

# ── Récupération du profil Yahoo Finance ─────────────────────────────────────
# Utilise le package yahoofinancer (CRAN) → à ajouter dans package.R :
#   if (!require("yahoofinancer")) install.packages("yahoofinancer")
get_yahoo_profile <- function(tk) {
  tryCatch({
    stock   <- yahoofinancer::Ticker$new(tk)
    profile <- stock$asset_profile
    desc    <- profile$longBusinessSummary
    sector  <- profile$sector %||% ""
    industry <- profile$industry %||% ""

    if (is.null(desc) || nchar(desc) < 10) {
      return(paste0(tk, " — No description available from Yahoo Finance."))
    }
    desc
  }, error = function(e) {
    # Fallback rvest si yahoofinancer échoue
    tryCatch({
      url  <- paste0("https://finance.yahoo.com/quote/", tk, "/profile/")
      page <- rvest::read_html(url)
      desc <- page %>%
        rvest::html_element("section[data-testid='description'] p") %>%
        rvest::html_text2()
      if (is.na(desc) || nchar(desc) < 10) stop("empty")
      desc
    }, error = function(e2) {
      paste0(tk, " — Description unavailable.")
    })
  })
}

# Récupération anticipée (une seule fois)
yahoo_about <- get_yahoo_profile(ticker)

# ── Helpers UI ────────────────────────────────────────────────────────────────
series_info_box <- function(source_html, frequency, adjustment, about) {
  htmltools::HTML(paste0('
  <div class="info-card">
    <div class="info-grid">
      <div class="info-row">
        <span class="info-label">Source</span>
        <span class="info-value">', source_html, '</span>
      </div>
      <div class="info-row">
        <span class="info-label">Frequency</span>
        <span class="info-value">', frequency, '</span>
      </div>
      <div class="info-row">
        <span class="info-label">Adjustment</span>
        <span class="info-value">', adjustment, '</span>
      </div>
    </div>
    <div class="info-about">', about, '</div>
  </div>
  '))
}

section_label <- function(icon, text) {
  htmltools::HTML(paste0(
    '<div class="section-label"><span class="section-icon">', icon,
    '</span><span class="section-text">', text, '</span></div>'))
}

subsection_label <- function(text) {
  htmltools::HTML(paste0('<div class="subsection-label">', text, '</div>'))
}

chart_note <- function(text) {
  htmltools::HTML(paste0('<p class="chart-note">', text, '</p>'))
}
```

<!-- ####################################################################### -->
<!-- Head Title                                                               -->
<!-- ####################################################################### -->

```{=html}
<!-- ── MASTHEAD ────────────────────────────────────────────────────────────── -->
<div class="masthead">
  <div class="masthead-eyebrow">Equity Research · Custom Analysis</div>
  <div class="masthead-title">Stock Report <span>— `r ticker`</span></div>
  <div class="masthead-date">Report date: `r format(Sys.Date(), '%B %d, %Y')`</div>
</div>
```

<!-- ####################################################################### -->
<!-- Abstract                                                                 -->
<!-- ####################################################################### -->

## Abstract

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">Abstract</div>
  </div>
</div>
```

```{=html}
<div class="abstract-box">
<p>This report delivers a structured equity analysis of <strong>`r ticker`</strong>, generated automatically from Yahoo Finance data.</p>

<p>Each company is examined through a consistent framework:</p>

<ul>
  <li><strong>Technical Analysis</strong> — Full indicator suite covering momentum (RSI, MACD), trend strength (ADX, Aroon), and volume flow (OBV, A/D Line), displayed over the full history and the trailing twelve months.</li>
  <li><strong>Yield Distribution</strong> — Histogram of daily log-returns characterizing the stock's historical return distribution and tail behavior.</li>
  <li><strong>Risk Metrics</strong> — A set of rolling risk indicators computed on a 252-day window: annualized volatility, Sharpe ratio, historical Value at Risk (1%), maximum drawdown, skewness, and excess kurtosis.</li>
  <li><strong>Financial Statements</strong> — Annual and quarterly income statement, balance sheet, and cash flow statement (in millions of USD) for a complete fundamental assessment.</li>
</ul>
</div>
```

<!-- ####################################################################### -->
<!-- Stock Section                                                            -->
<!-- ####################################################################### -->

## `r ticker`

```{=html}
<div class="company-hero">
  <div class="co-body">
    <div class="masthead-title">`r ticker`</div>
  </div>
</div>
```

```{r INFO_BOX, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
series_info_box(
  source_html = paste0('Yahoo Finance — <a href="https://finance.yahoo.com/quote/', ticker,
                       '/" target="_blank">link</a> · ',
                       '<a href="https://finance.yahoo.com/quote/', ticker,
                       '/profile/" target="_blank">profile</a>'),
  frequency   = "Daily",
  adjustment  = "Not Adjusted",
  about       = yahoo_about
)
```

### Technical Analysis

#### *Full*

```{=html}
<div class="perf-section">
```

```{r TI_FULL, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
tagList(
  div(style = "display:flex; justify-content:center; width:100%;",
      produce_technical_indicators_plot(
        id = ticker, interval = "1Y", title = paste0(ticker, ", Share"),
        technical_indicator = NULL, cut = FALSE) %>%
        hc_size(height = 900) %>%
        hc_chart(marginRight = 20, marginLeft = 100)),
  HTML('<p class="chart-note" style="color:white;">Technical indicators computed on the full dataset — SMA 20/50/200, Volume, ADX, Aroon, MACD, RSI(14), Stochastic</p>'))
```

```{=html}
</div>
```

#### *Last Year*

```{=html}
<div class="perf-section">
```

```{r TI_1Y, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
tagList(
  div(style = "display:flex; justify-content:center; width:100%;",
      produce_technical_indicators_plot(
        id = ticker, interval = "1Y", title = paste0(ticker, ", Share"),
        technical_indicator = NULL, cut = TRUE) %>%
        hc_size(height = 900) %>%
        hc_chart(marginRight = 20, marginLeft = 100)),
  HTML('<p class="chart-note" style="color:white;">Technical indicators computed on the last year of data — SMA 20/50/200, Volume, OBV, A/D Line, ADX, Aroon, MACD, RSI(14), Stochastic</p>'))
```

```{=html}
</div>
```

### Yield Distribution

```{=html}
<div class="perf-section">
```

```{r YIELD_DIST, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
data <- compute_risk_return(id = ticker, days = c(1), window = 252, rf = 0.04)
data1 <- data %>% select(id, time, logret_1d)

tagList(
  div(style = "display:flex; justify-content:center;",
      produce_histogram_plot(df = data1, date_col = "time", value_col = "logret_1d",
                             title = paste0(ticker, ", 1-Day Yield, across time"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">The 1-day log return is a cornerstone metric in quantitative finance. Unlike simple returns, log returns are time-additive: \\(r_{t_1, t_n} = \\sum_{i=1}^{n} r_{t_i}\\), and they approximate normality for small daily moves — \\(r_t = \\ln\\left(\\frac{P_t}{P_{t-1}}\\right)\\).</p>'),
  produce_distribution_plot(df = data1, value_col = "logret_1d",
                            title = paste0(ticker, ", 1-Day Yield, distribution")),
  HTML('<p class="chart-note" style="color:white; text-align:center;">The 1-day log return captures the relative change in price: \\(r_t = \\ln\\left(\\frac{P_t}{P_{t-1}}\\right)\\). Log returns are often analyzed as a distribution, which tends to be approximately symmetric and bell-shaped for small daily moves.</p>'))
```

```{=html}
</div>
```

### Annualized Volatility

```{=html}
<div class="perf-section">
```

```{r VOL, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
data1 <- data %>% select(id, time, ann_vol_logret_1d_252d_rolling)

tagList(
  div(style = "display:flex; justify-content:center;",
      produce_histogram_plot(df = data1, date_col = "time",
                             value_col = "ann_vol_logret_1d_252d_rolling",
                             title = paste0(ticker, ", Annualized Volatility (1Y Rolling)"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">Annualized volatility measures the dispersion of daily log returns scaled to a yearly horizon: \\(\\sigma_{ann} = \\sigma_{daily} \\times \\sqrt{252}\\). Computed on a 252-day rolling window.</p>'))
```

```{=html}
</div>
```

### Sharpe Ratio

```{=html}
<div class="perf-section">
```

```{r SHARPE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
data1 <- data %>% select(id, time, sharpe_1d_252d_rolling)

tagList(
  div(style = "display:flex; justify-content:center;",
      produce_histogram_plot(df = data1, date_col = "time",
                             value_col = "sharpe_1d_252d_rolling",
                             title = paste0(ticker, ", Sharpe Ratio (1Y Rolling), Rf = 4%"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">The Sharpe ratio measures risk-adjusted return: \\(S = \\frac{\\bar{r} - r_f}{\\sigma_{ann}}\\). Values above 1 indicate attractive risk-adjusted performance.</p>'))
```

```{=html}
</div>
```

### Value at Risk (1%)

```{=html}
<div class="perf-section">
```

```{r VAR, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
data1 <- data %>% select(id, time, var1pct_logret_1d_252d_rolling)

tagList(
  div(style = "display:flex; justify-content:center;",
      produce_histogram_plot(df = data1, date_col = "time",
                             value_col = "var1pct_logret_1d_252d_rolling",
                             title = paste0(ticker, ", Historical VaR 1% (1Y Rolling)"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">Value at Risk at the 1% level: \\(\\text{VaR}_{1\\%} = \\text{Quantile}_{1\\%}(r_t)\\). A VaR of −3% means that on 1 out of 100 trading days, the loss exceeds 3%.</p>'))
```

```{=html}
</div>
```

### Maximum Drawdown

```{=html}
<div class="perf-section">
```

```{r MDD, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
data1 <- data %>% select(id, time, max_drawdown_1d_252d_rolling)

tagList(
  div(style = "display:flex; justify-content:center;",
      produce_histogram_plot(df = data1, date_col = "time",
                             value_col = "max_drawdown_1d_252d_rolling",
                             title = paste0(ticker, ", Maximum Drawdown (1Y Rolling)"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">Maximum Drawdown measures the largest peak-to-trough decline: \\(\\text{MDD} = \\frac{\\min(P_t) - \\max(P_s)}{\\max(P_s)}, \\; s \\leq t\\).</p>'))
```

```{=html}
</div>
```

### Skewness

```{=html}
<div class="perf-section">
```

```{r SKEW, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
data1 <- data %>% select(id, time, skew_logret_1d_252d_rolling)

tagList(
  div(style = "display:flex; justify-content:center;",
      produce_histogram_plot(df = data1, date_col = "time",
                             value_col = "skew_logret_1d_252d_rolling",
                             title = paste0(ticker, ", Skewness (1Y Rolling), across time"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">Skewness measures the asymmetry of the return distribution: \\(\\text{Skew} = \\frac{1}{n}\\sum_{t=1}^{n}\\left(\\frac{r_t - \\bar{r}}{\\sigma}\\right)^3\\). A negative skew signals that large losses occur more frequently than large gains.</p>'),
  div(style = "display:flex; justify-content:center;",
      produce_distribution_plot(df = data1, value_col = "skew_logret_1d_252d_rolling",
                                title = paste0(ticker, ", Skewness (1Y Rolling), distribution"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">A negative skew (e.g. −0.5) means the distribution has a longer left tail, indicating more frequent extreme low values.</p>'))
```

```{=html}
</div>
```

### Kurtosis

```{=html}
<div class="perf-section">
```

```{r KURT, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
data1 <- data %>% select(id, time, kurt_logret_1d_252d_rolling)

tagList(
  div(style = "display:flex; justify-content:center;",
      produce_histogram_plot(df = data1, date_col = "time",
                             value_col = "kurt_logret_1d_252d_rolling",
                             title = paste0(ticker, ", Excess Kurtosis (1Y Rolling)"))),
  HTML('<p class="chart-note" style="color:white; text-align:center;">Excess kurtosis: \\(\\text{Kurt} = \\frac{1}{n}\\sum_{t=1}^{n}\\left(\\frac{r_t - \\bar{r}}{\\sigma}\\right)^4 - 3\\). A value of 0 matches a normal distribution; positive excess kurtosis indicates fat tails.</p>'))
```

```{=html}
</div>
```

### Financial Statements

#### *Income Statement*

<div class="perf-section">
<ul>
<li><strong>Total Revenue:</strong> Total money earned from selling products and services. <em>Unit: Millions $</em></li>
<li><strong>Gross Profit:</strong> Revenue minus direct production costs. <em>Unit: Millions $</em></li>
<li><strong>Research and Development:</strong> Investment in new products and technologies. <em>Unit: Millions $</em></li>
<li><strong>Operating Income:</strong> Profit from core operations before interest and taxes. <em>Unit: Millions $</em></li>
<li><strong>Net Income:</strong> Final profit after all expenses, interest and taxes. <em>Unit: Millions $</em></li>
<li><strong>EBITDA:</strong> Operating profit before depreciation and amortization. <em>Unit: Millions $</em></li>
<li><strong>EPS (Diluted):</strong> Net income per share including all dilutive securities. <em>Unit: $ per share</em></li>
<li><strong>Gross Margin / Operating Margin / Net Margin:</strong> Profitability ratios. <em>Unit: %</em></li>
<li><strong>Market Capitalization:</strong> Total market value of the company. <em>Unit: Millions $</em></li>
</ul>
</div>

```{=html}
<div class="perf-section">
```

```{r FS_IS_A, echo=FALSE, results='asis', warning=FALSE, message=TRUE}
tryCatch(
  produce_financial_statements_table(id = ticker, aq = "A", fs = "I",
                                     title = "Income Statement — Annual"),
  error = function(e) message("No Income Statement available"))
```

```{=html}
</div>
<div class="perf-section">
```

```{r FS_IS_Q, echo=FALSE, results='asis', warning=FALSE, message=TRUE}
tryCatch(
  produce_financial_statements_table(id = ticker, aq = "Q", fs = "I",
                                     title = "Income Statement — Quarter"),
  error = function(e) message("No Income Statement available"))
```

```{=html}
</div>
```

#### *Balance Sheet*

<div class="perf-section">
<ul>
<li><strong>Cash & Short Term Investments:</strong> Immediate liquidity available. <em>Unit: Millions $</em></li>
<li><strong>Total Assets / Total Liabilities / Total Equity:</strong> Core balance sheet items. <em>Unit: Millions $</em></li>
<li><strong>Long Term Debt:</strong> Obligations due beyond one year. <em>Unit: Millions $</em></li>
<li><strong>ROA / ROE / ROIC:</strong> Return metrics. <em>Unit: %</em></li>
<li><strong>Current / Quick / Cash Ratio:</strong> Liquidity ratios. <em>Unit: Ratio (x)</em></li>
<li><strong>Debt-to-Equity / Net Debt / EBITDA:</strong> Leverage ratios. <em>Unit: Ratio (x)</em></li>
</ul>
</div>

```{=html}
<div class="perf-section">
```

```{r FS_BS_A, echo=FALSE, results='asis', warning=FALSE, message=TRUE}
tryCatch(
  produce_financial_statements_table(id = ticker, aq = "A", fs = "B",
                                     title = "Balance Sheet — Annual"),
  error = function(e) message("No Balance Sheet available"))
```

```{=html}
</div>
<div class="perf-section">
```

```{r FS_BS_Q, echo=FALSE, results='asis', warning=FALSE, message=TRUE}
tryCatch(
  produce_financial_statements_table(id = ticker, aq = "Q", fs = "B",
                                     title = "Balance Sheet — Quarter"),
  error = function(e) message("No Balance Sheet available"))
```

```{=html}
</div>
```

#### *Cash Flow*

<div class="perf-section">
<ul>
<li><strong>Cash from Operating Activities:</strong> Actual cash generated by core business. <em>Unit: Millions $</em></li>
<li><strong>Free Cash Flow:</strong> Operating cash minus capex. <em>Unit: Millions $</em></li>
<li><strong>Capital Expenditures:</strong> Cash spent on physical assets (negative = outflow). <em>Unit: Millions $</em></li>
<li><strong>Share Buybacks:</strong> Cash used to repurchase own shares (negative = outflow). <em>Unit: Millions $</em></li>
<li><strong>Price to Free Cash Flow:</strong> Valuation multiple on FCF. <em>Unit: Ratio (x)</em></li>
</ul>
</div>

```{=html}
<div class="perf-section">
```

```{r FS_CF_A, echo=FALSE, results='asis', warning=FALSE}
tryCatch(
  produce_financial_statements_table(id = ticker, aq = "A", fs = "C",
                                     title = "Cash Flow Statement — Annual"),
  error = function(e) message("No Cash Flow Statement available"))
```

```{=html}
</div>
<div class="perf-section">
```

```{r FS_CF_Q, echo=FALSE, results='asis', warning=FALSE}
tryCatch(
  produce_financial_statements_table(id = ticker, aq = "Q", fs = "C",
                                     title = "Cash Flow Statement — Quarter"),
  error = function(e) message("No Cash Flow Statement available"))
```

```{=html}
</div>
```
